Many Analystis Project

### 2022-03-12 History/analysis.Rmd
order files
create history foldrer

## degroup variables for within and between analysis
## https://cran.r-project.org/web/packages/parameters/vignettes/demean.html
d1 <-
  cbind(d1,
        parameters::demean(d1, select = c("anx", "ch", "bg"), group = "country"))

hist(d1$anx)
```

@@

-   religion + ses + male + country + a different unmeasured latent variable1 (e.g. privilege) affects distress.

@@

## Dag graph

>>>>

## degroup variables for within and between analysis
## https://cran.r-project.org/web/packages/parameters/vignettes/demean.html
# d1 <-
#   cbind(d1,
#         parameters::demean(d1, select = c("anx", "ch", "bg"), group = "country"))

#hist(d1$anx)
```

@@

-   religion + ses + male + country + ses

@@

## DAG graph
